---
title: "group2_client2_evelyn"
author: "Hanzhang Song"
date: "2023-02-09"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading data

```{r}
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
raw_data <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx")
```

## Q1: Is there a particular demographic that is scoring higher in PSQ?

```{r}
df1 <- raw_data[c(1,77:89)]
names(df1) <- df1[1,]
df1 <- df1[-1,]
names(df1)[1] <- "Participant"
```

```{r}
df1 <- na.omit(df1)
# Program Year
df1$`PSQ Score` <- as.numeric(df1$`PSQ Score`)
ggplot(df1, aes(x = `PSQ Score`, y = `Program Year`, fill = `Program Year`)) + 
  geom_boxplot()

# Age
ggplot(df1, aes(x = `PSQ Score`, y = Age, fill = Age)) + 
  geom_boxplot()

# Location
ggplot(df1, aes(x = `PSQ Score`, y = Location)) + 
  geom_boxplot()

# Race
ggplot(df1, aes(x = `PSQ Score`, y = `Which of the following best describes you? (select all that apply)`)) + 
  geom_boxplot() + 
  ylab("Race")

# Transgender or not
ggplot(df1, aes(x = `PSQ Score`, y = `Do you identify as transgender?`)) + 
  geom_boxplot() + 
  ylab("Transgender or not")

# Gender
ggplot(df1, aes(x = `PSQ Score`, y = `Which of the following best describes your gender?`)) + 
  geom_boxplot() + 
  ylab("Gender")

# Sexual orientation
ggplot(df1, aes(x = `PSQ Score`, y = `What is your sexual orientation?`)) + 
  geom_boxplot() + 
  ylab("Sexual Orientation")

# Relationship status
ggplot(df1, aes(x = `PSQ Score`, y = `What best describes you relationship status?`)) + 
  geom_boxplot() + 
  ylab("Relationship status")

# Having children or not
ggplot(df1, aes(x = `PSQ Score`, y = `Do you have any children?`)) + 
  geom_boxplot() + 
  ylab("Having children or not")

# Relocation
ggplot(df1, aes(x = `PSQ Score`, y = `Did you relocate to attend your program?`)) + 
  geom_boxplot() + 
  ylab("Relocation")

# Income
ggplot(df1, aes(x = `PSQ Score`, y = `Do you identify as coming from low socioeconomic status?`)) + 
  geom_boxplot() + 
  ylab("Income")

# Working hours
ggplot(df1, aes(x = `PSQ Score`, y = `Do you work while enrolled in your program support yourself?`)) + 
  geom_boxplot() + 
  ylab("Working hours")
```

## Q2: Is there a particular stressor(eg. academic, financial, etc) that is rated higher?

```{r}
df2 <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "Stress Questions")
names(df2) <- df2[1,]
df2 <- df2[-1,]
names(df2)[1] <- "Participant"
```

```{r}
df2 <- na.omit(df2)
ggplot(data = df2, aes(`Financial stress`, fill = `Financial stress`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) + 
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Physical health stress`, fill = `Physical health stress`)) + 
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Relationship stress`, fill = `Relationship stress`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Family stress`, fill = `Family stress`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Academic stress`, fill = `Academic stress`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Minority stress`, fill = `Minority stress`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))

ggplot(data = df2, aes(`Grief and/or loss`, fill = `Grief and/or loss`)) +
  geom_bar() + 
  scale_fill_manual(values = c("#91bad6","#528aae","#bcdae8","#1e3f66")) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -1, colour = "black") + 
  scale_x_discrete(limits = c("Severe stress", "Moderate stress", "Mild stress", "None"))
```

## Q3: What are the most utilized forms of self-care?

```{r}
# We have 217 responses from exercises, 210 for therapy frequencies, 523 for socializing frequencies, and 61 for spiritual, and 186 for others.
raw_data %>%
  group_by(Q88_3_TEXT) %>%
  summarise(Count = n())
# Reading, singing, and video games have more than one responses.
```

## Q4: Is there a difference in overall empathy scores between 1st and 2nd years?

```{r}
df4 <- raw_data[c(1,77,89:94)]
names(df4) <- df4[1,]
df4 <- df4[-1,]
names(df4)[1] <- "Participant"
```

```{r}
df4 <- na.omit(df4)
df4$`PSQ Score` <- as.numeric(df4$`PSQ Score`)
df4$`IRI Score` <- as.numeric(df4$`IRI Score`)
df4$`IRI- Fantasy scale` <- as.numeric(df4$`IRI- Fantasy scale`)
df4$`IRI- Empathy Concern` <- as.numeric(df4$`IRI- Empathy Concern`)
df4$`IRI- Personal Distress` <- as.numeric(df4$`IRI- Personal Distress`)
df4$`IRI- Perspective Taking` <- as.numeric(df4$`IRI- Perspective Taking`)
```

```{r}
ggplot(df4, aes(x = `Program Year`, y = `IRI Score`, fill = `Program Year`)) + 
  geom_boxplot()
```

## Q5: Is there a difference between 1st and 2nd years IRI scores when just considering subscales?

```{r}
df5 <- df4[c(1,2,5:7)]
df5 <- na.omit(df5)

ggplot(df5, aes(x = `Program Year`, y = `IRI- Fantasy scale`, fill = `Program Year`)) + 
  geom_boxplot()
ggplot(df5, aes(x = `Program Year`, y = `IRI- Empathy Concern`, fill = `Program Year`)) + 
  geom_boxplot()
ggplot(df5, aes(x = `Program Year`, y = `IRI- Perspective Taking`, fill = `Program Year`)) + 
  geom_boxplot()

df5 <- df5 %>%
  mutate(`Empathy Concern + Perspective Taking` = 
           rowSums(across(c("IRI- Empathy Concern", "IRI- Perspective Taking"))),
         `Empathy Concern + Perspective Taking + Fantasy scale` = 
           rowSums(across(c("IRI- Fantasy scale", "IRI- Empathy Concern", "IRI- Perspective Taking"))))

ggplot(df5, aes(x = `Program Year`, y = `Empathy Concern + Perspective Taking`, fill = `Program Year`)) + 
  geom_boxplot()
ggplot(df5, aes(x = `Program Year`, y = `Empathy Concern + Perspective Taking + Fantasy scale`, fill = `Program Year`)) + 
  geom_boxplot()
```

## Q6: Is there a difference in stress scores between 1st and 2nd years?

```{r}
df6 <- df4[c(1:3)]
df6 <- na.omit(df6)
ggplot(df6, aes(x = `PSQ Score`, y = `Program Year`)) + geom_boxplot()
```

## Q7: Is there a particular demographic that is scoring higher in PSQ?

```{r}
demo <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "Demographics")
psq <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "PSQ")
iri <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "IRI")
```

```{r}
names(demo) <- demo[1,]
demo <- demo[-1,]
names(demo)[1] <- "Participant"

names(psq) <- psq[1,]
psq <- psq[-1,]
names(psq)[1] <- "Participant"

names(iri) <- iri[1,]
iri <- iri[-1,]
names(iri)[1] <- "Participant"

psq <- psq[22]
iri <- iri[c(30:34)]
df7 <- cbind(demo,psq,iri)
```

```{r}
df7 <- df7 %>% 
  mutate_at(c('PSQ Score', 'IRI Score', 'IRI- FS', 'IRI- EC', 'IRI- PD', 'IRI- PT'),
            as.numeric)
```

```{r}
# First year = 1, second year = 0
year <- ifelse(df7$`Program Year` == 'Current first year', 1, 0)

df_py <- data.frame(Year = year,
                    PSQ = df7$`PSQ Score`)

fit.year = lm(formula = PSQ ~ Year, data = df_py)
summary(fit.year)
```

```{r}
# Age range
age.order <- factor(df7$`Age range`)

df_age <- data.frame(Age = age.order,
                    PSQ = df7$`PSQ Score`)

fit.age = lm(formula = PSQ ~ Age, data = df_age)
summary(fit.age)
```

```{r}
# Program Location
loc.order <- factor(df7$`Program Location`)

df_loc <- data.frame(Reg = loc.order,
                    PSQ = df7$`PSQ Score`)

fit.loc = lm(formula = PSQ ~ Reg, data = df_loc)
summary(fit.loc)
```

```{r}
# Race
eth.order <- factor(df7$`Race/Ethnicity`)

df_eth <- data.frame(Race = eth.order,
                    PSQ = df7$`PSQ Score`)

fit.eth = lm(formula = PSQ ~ Race, data = df_eth)
summary(fit.eth)
```

```{r}
# Trans
trans.order <- factor(df7$Transgender)

df_trans <- data.frame(Trans = trans.order,
                    PSQ = df7$`PSQ Score`)

fit.trans = lm(formula = PSQ ~ Trans, data = df_trans)
summary(fit.trans)
```

```{r}
# Gender
sex.order <- factor(df7$Gender)

df_sex <- data.frame(Sex = sex.order,
                    PSQ = df7$`PSQ Score`)

fit.sex = lm(formula = PSQ ~ Sex, data = df_sex)
summary(fit.sex)
```

```{r}
# Sexual orientation
ori.order <- factor(df7$`Sexual orientation`)

df_ori <- data.frame(Ori = ori.order,
                    PSQ = df7$`PSQ Score`)

fit.ori = lm(formula = PSQ ~ Ori, data = df_ori)
summary(fit.ori)
```

```{r}
# Relationship status
rel.order <- factor(df7$`Relationship status`)

df_rel <- data.frame(Rel = rel.order,
                    PSQ = df7$`PSQ Score`)

fit.rel = lm(formula = PSQ ~ Rel, data = df_rel)
summary(fit.rel)
```

```{r}
# Have kids = 1, no = 0
kids <- ifelse(df7$`Have Kids` == 'Yes', 1, 0)

df_kids <- data.frame(Kids = kids,
                    PSQ = df7$`PSQ Score`)

fit.kids = lm(formula = PSQ ~ Kids, data = df_kids)
summary(fit.kids)
```

```{r}
# Relocate = 1, no = 0
move <- ifelse(df7$Relocate == 'Yes', 1, 0)

df_move <- data.frame(Move = move,
                    PSQ = df7$`PSQ Score`)

fit.move = lm(formula = PSQ ~ Move, data = df_move)
summary(fit.move)
```

```{r}
# Low ses = 1, no = 0
ses <- ifelse(df7$`Low SES` == 'Yes', 1, 0)

df_ses <- data.frame(Ses = ses,
                    PSQ = df7$`PSQ Score`)

fit.ses = lm(formula = PSQ ~ Ses, data = df_ses)
summary(fit.ses)
```

```{r}
# Working
work.order <- factor(df7$Working)

df_work <- data.frame(Work = work.order,
                    PSQ = df7$`PSQ Score`)

fit.work = lm(formula = PSQ ~ Work, data = df_work)
summary(fit.work)
```

## Q8: Is it possible to obtain a visual for PSQ vs specific demographics in particular?

```{r}
# PSQ vs. low SES
df8 <- df7[c(1,12,14)]
df8 <- df8[df8$`Low SES` == 'No',]
hist(df8$`PSQ Score`, main = "Histogram of PSQ for Low SES",
     xlab = "PSQ Score", col = "#FFF0A5", border = "#9BD6E6")
hist(df8$`PSQ Score`, main = "Histogram of PSQ for non-low SES",
     xlab = "PSQ Score", col = "#D49AB3", border = "#7A93B2")
```

```{r}
# PSQ vs. sexual orientation
ggplot(df1, aes(x = `PSQ Score`, y = `What is your sexual orientation?`)) + 
  geom_boxplot() + 
  ylab("Sexual Orientation")
```

```{r}
# PSQ in males vs. females
ggplot(df1, aes(x = `PSQ Score`, y = `Which of the following best describes your gender?`)) + 
  geom_boxplot() + 
  ylab("Gender")
```

```{r}
# PSQ vs. Race
ggplot(df1, aes(x = `PSQ Score`, y = `Which of the following best describes you? (select all that apply)`)) + 
  geom_boxplot() + 
  ylab("Race")
```

## Q9: Self-care visuals

```{r}
df9 <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "Self Care (Cleaned)")
names(df9) <- df9[1,]
df9 <- df9[-1,]
names(df9)[1] <- "Participant"
df9 <- cbind(df9,psq)
df9$`PSQ Score` <- as.numeric(df9$`PSQ Score`)
```

```{r}
# PSQ vs. any exercise
ggplot(df9, aes(x = `PSQ Score`, y = `Any exercise?`)) + geom_boxplot()
```

```{r}
# PSQ vs. any spiritual
ggplot(df9, aes(x = `PSQ Score`, y = `Any spiritual?`)) + geom_boxplot()
```

```{r}
# PSQ vs. any other
ggplot(df9, aes(x = `PSQ Score`, y = `Any Other?`)) + geom_boxplot()
```

```{r}
fit.1 <- lm(`IRI Score` ~ `PSQ Score`, data = df7)
summary(fit.1)
ggp <- ggplot(df7, aes(`PSQ Score`, `IRI Score`)) +           
  geom_point()
ggp +                                     
  stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth")
# Residual plot
res <- resid(fit.1)
plot(fitted(fit.1), res)
abline(0,0)
```

# IRI Calculation
```{r}
df10 <- df4 %>%
  mutate(`4 subscales sum` = 
           rowSums(across(c("IRI- Empathy Concern", "IRI- Perspective Taking", "IRI- Fantasy scale", "IRI- Personal Distress"))))
df10 <- df10[c(1,4:9)]
```


# ANOVA: IRI vs. Program Year
```{r}
year <- ifelse(df7$`Program Year` == 'Current first year', 1, 0)

iri_py <- data.frame(Year = year,
                    IRI = df7$`IRI Score`)

fit.3 <- lm(formula = IRI ~ Year, data = iri_py)
summary(fit.3)
```

```{r}
df11 <- df4[df4$`Program Year` == 'Current first year',]
hist(df11$`PSQ Score`, main = "Histogram of PSQ for 1st year",
     xlab = "PSQ Score", col = "#D49AB3", border = "#7A93B2")
```

```{r}
df9 <- read_excel("~/Desktop/BU/MSSP/MA 676/consulting/c2/Stress, Empathy and Self-care_MASTER.xlsx", sheet = "Self Care (Cleaned)")
names(df9) <- df9[1,]
df9 <- df9[-1,]
names(df9)[1] <- "Participant"
`Program Year` <- df7$`Program Year`
df9 <- cbind(df9,psq,iri,`Program Year`)
df9$`IRI Score` <- as.numeric(df9$`IRI Score`)
df9$`PSQ Score` <- as.numeric(df9$`PSQ Score`)
df9$`Therapy frequency` <- as.numeric(df9$`Therapy frequency`)
```

```{r}
aov1 <- aov(`IRI Score` ~ `Program Year` + `PSQ Score` + `Any exercise?` + `Therapy frequency`, data = df9)
summary.lm(aov1)

resd <- resid(aov1)
plot(fitted(aov1), resd)
abline(0,0)

iri_aov_augment <- broom::augment(aov1, df9)
ggplot(iri_aov_augment, aes(sample = .resid)) + 
  labs(title = "QQ Plot for residuals of IRI vs. Program Year",
       x = "theoretical", y = "sample") + 
  geom_qq() + 
  geom_qq_line()
```


```{r}
fit.4 <- lm(`IRI Score` ~ `Program Year` + `PSQ Score` + `Any exercise?` + `Therapy frequency`, data = df9)
summary(fit.4)
```

```{r}
fit.5 <- lm(`IRI Score` ~ `PSQ Score` + `Any exercise?` + `Therapy frequency`, data = df9)
summary(fit.5)
resid <- resid(fit.5)
plot(fitted(fit.5), resid)
abline(0,0)
```

```{r}
library(lmtest)
lrtest(fit.4,fit.5)
```







```{r}
aov2 <- aov(`PSQ Score` ~ `Program Year`, data = df7)
summary.lm(aov2)

psq_aov_augment <- broom::augment(aov2, df7)
ggplot(psq_aov_augment, aes(sample = .resid)) + 
  labs(title = "QQ Plot for residuals of PSQ vs. Program Year",
       x = "theoretical", y = "sample") + 
  geom_qq() + 
  geom_qq_line()
```





